### 2019-05-25 doc/chapters/towards_verifying.tex
fixed grammer

Next we ensure, that the result is the same value as \emph{this}.
\begin{lstlisting}
  ensuring(res => res.satoshis == this.satoshis)
\end{lstlisting}
Here, we can directly use equals (==) on Satoshis, because its a case class and Int64, the only parameter of Satoshis is a case class too.

After writing the verification, we ran Stainless on the source files.
It prints a lot of errors because of code incompatibility.
So we had to rewrite it as described in the following sections.

>>>>

To ensure that the result is the same value as \emph{this}:
\begin{lstlisting}
  ensuring(res => res.satoshis == this.satoshis)
\end{lstlisting}
Here, one can directly use equals (==) on Satoshis, because its a case class and Int64, the only parameter of Satoshis is a case class too.

After writing the verification, running Stainless on the source files was the next step.
It prints a lot of errors because of code incompatibility.
So lets describe the code rewriting in the following sections.
